---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Usage

There are three ways to use scID. 

### Usage 1: Canonical usage (for finding equivalent groups of cells across data)
Given two datasets of single-cell RNA-seq gene expression for which cell grouping for one the datasets (reference) is known, scID seeks to find transcriptionally equivalent groups of cells for the second dataset (target).
```
scID_output <- scID::scid_multiclass(target_gem, reference_gem, reference_clusters, ...)
```

#### Input
1. ```target_gem``` An nxm data frame of n genes (rows) in m cells (columns) of the dataset with unknown grouping, where each entry is library-depth or column normalized gene expression. Cell names are expected to be unique.
2. ```reference_gem``` An NxM data frame of N genes (rows) in M cells (columns) of the dataset with known grouping, where each entry is library-depth or column normalized gene expression. 
3. ```reference_clusters``` A list of cluster labels for the reference cells.

#### Output

scID_output is a list of two objects 

1. ```scID_output$labels``` A named list of cluster labels for the target cells

2. ```scID_output$markers``` A data frame of signature genes extracted from the reference clusters. 

### Usage 2: Canonical usage (for finding equivalent groups of cells across data) with multiple targets (T1, T2)

* Step 1: Extract markers from reference clusters
```
markers_generated_by_scID <- scID::find_markers(reference_gem, reference_clusters, logFC)
```
This step can be skipped when the user has own method for extracting markers. 

* Step 2: Find transctiptionally equivalent cells in target datasets
```
scID_output_T1 <- scID:scid_multiclass(T1, markers_generated_by_scID, ...)

scID_output_T2 <- scID::scid_multiclass(T2, markers_generated_by_scID, ...)
```
### Usage 3: User-specified cluster gene signatures
A pre-computed set of markers can be given as input by the user alternatively. The markers object has to be a data frame with genes and cluster ID in columns as in [this](https://github.com/BatadaLab/scID/blob/master/ExampleData/markers.rds) example file.
```
scID_output <- scID::scid_multiclass(T, markers_generated_by_user, ...)
```














Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
